\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-08-16 sections/coverpage.tex
Update title options

  \vspace*{\fill}
  { \huge \bfseries Correlating Microbial Abundances for the Microbial Interaction Network Database}\\[0.4cm] % Title of your document

>>>>

  \vspace*{\fill}
  { \huge  1. Investigating the best practices for inference of microbial co-occurrence networks from 16S data}\\[0.4cm] % Title of your document
  { \huge  2. Attempting to find the best practice pipeline for inferring co-occurrence networks from 16S data}\\[0.4cm] % Title of your document
  { \huge  3. Deciphering the complexities in co-occurrence network inference from 16S data}\\[0.4cm] % Title of your document
